Constant-round Blind Classical Verification of Quantum Sampling

### 2020-07-30 qpip0.tex
Smooth out binding property proof

\begin{theorem}[binding property of $\PiNaive$]
	\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting (ie. $y\ne\bot$), $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
\end{theorem}
\begin{proof}
	There's a \emph{dummy strategy} for $\PiNaive$'s prover, who chooses $\rho$ as maximally mixed state instead, and executes the rest of the protocol honestly.
	It is accepted in the testing round with probability $1-\negl(\lambda)$,
	but has negligible probability passing the verification after the Hadamard round.

	\Ethan{Smooth this out}

	Consider the following reduction to another cheating $\BQP$ prover for $\PiNaive$ that is perfect and non-aborting.

	We define $\Pstar$ as follows.
	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
	If $y\ne\bot$, then reply $y$;
	else, run the corresponding step of the dummy strategy as in \Cref{lem:trivial-4-round-strategy} and reply with its results.
	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
	else, continue the dummy strategy.

@@

	Now we relate $(d', z')$ back to $(d, z)$.
	First, for the case that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
	we have $(d', z')\approx_{c, O(\eps)}(\Rej, \bot)=(d, z)$ conditioned on $\PNaiveStar$ aborts.
	For the other case, conditioned on $\PNaiveStar$ not aborts, clearly $(d, z)=(d', z')$.
	So we have $(d, z)\approx_{c, O(\varepsilon)}(d', z')\approx_{c, \negl(\lambda)}(d', z_{ideal}')$,
	which in turn implies $\abs{d-d'}\leq O(\eps)$
	and $(d, z_{ideal})\approx_{c, O(\eps)}(d', z_{ideal}')$.
	Combining everything, we conclude that $(d, z)\approx_{c, O(\eps)}(d, z_{ideal})$.
\end{proof}

@@

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.

>>>>

\begin{theorem}[binding property of $\PiNaive$]
	\label{lem:naive-qpip0-binding}
	Let $\PNaiveStar$ be a cheating $\BQP$ prover for $\PiNaive$ and $\lambda$ be the security parameter.
	Under the QLWE assumption, if conditioned on $\PNaiveStar$ not aborting (ie. $y\ne\bot$), $\PNaiveStar$ passes the testing round with probability $1-\negl(\lambda)$,
	then the verifier's output in the Hadamard round is $O(\eps)$-computationally indistinguishable from $(d, z_{ideal})$.
\end{theorem}
\begin{proof}
	If the prover chooses $\rho$ as the maximally mixed state and executes the rest of the protocol honestly,
	it would be accepted in the testing round with probability $1-\negl(\lambda)$,
	but has negligible probability passing the verification after the Hadamard round.
	We call this the \emph{dummy strategy}.

	Now we construct another cheating $\BQP$ prover $\Pstar$ that is perfect and non-aborting as follows.
	For the second message, run $(y, \sigma)\leftarrow\cPNaiveStar{2}(pk, \rho)$.
	If $y\ne\bot$, then reply $y$;
	else, run the corresponding step of the dummy strategy and reply with its results.
	For the fourth message, if $y\ne\bot$, run and reply with $a\leftarrow\cPNaiveStar{4}(pk, c, \sigma)$;
	else, continue the dummy strategy.

@@

	Now we relate $(d', z')$ back to $(d, z)$.
	First, conditioned on that $\PNaiveStar$ aborts, since dummy strategy will be rejected with overwhelming probability in Hadamard round,
	we have $(d', z')$ is $O(\varepsilon)$-computationally indistinguishable to $(\Rej, \bot)=(d, z)$.
	On the other hand, conditioned on $\PNaiveStar$ not aborting, clearly $(d, z)=(d', z')$.
	So $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d', z')$,
	which in turn is $\negl(\lambda)$-computationally indistinguishable to $d', z_{ideal}')$.
	So $\abs{d-d'}\leq O(\eps)$,
	and $(d, z_{ideal})$ is $O(\eps)$-computationally indistinguishable to $(d', z_{ideal}')$.
	Combining everything, we conclude that $(d, z)$ is $O(\eps)$-computationally indistinguishable to $(d, z_{ideal})$.
\end{proof}

@@

Now let $z_{true}$, as a mixed state, be correctly sampled from the $\SampBQP$ instance $D_x$,
and let $z_{ideal, i}=\tr(z_{good, i})z_{true}$.
We show that $z_{ideal, i}$ is close to $z_{good, i}$.
\begin{theorem}
	\label{thm:zgood-zideal}
	$\tr\abs{z_{good, i}-z_{ideal, i}}\leq O(\varepsilon)$
	\Ethan{This doesn't seem true; I think we get computational guarantees here at best?}
\end{theorem}
\begin{proof}
	For every $i\in [m]$ and every prover strategy $(U_0,U)$ for Protocol~\ref{proto:QPIP0samp}, consider the following composite strategy of the prover for the naive $\QPIP_0$ Protocol, Protocol~\ref{proto:qpip0_naive}. Note that the prover only interact with the verifier in Step~\ref{step:urmila-in-naive} of Protocol~\ref{proto:qpip0_naive} where Protocol~\ref{proto:urmila4} is run, so we describe the prover's action in turns of the four rounds of communication in Protocol~\ref{proto:urmila4}.
